Forschungsprojekt

### 2020-10-14 documentation/presentation/main.tex
:-)

\section{Evaluation}
\begin{multicols}{2}
\noindent 5 Machines, with
\begin{itemize}
	\item 96 cores, of which 48 virtual
	\item 256 GB of RAM each, one machine only 128 GB
	\item Ubuntu 18.04.2 LTS
\end{itemize}
\noindent Measurements:
\begin{itemize}
	\item \textbf{execution time}: time from start to finish of the console command
	\item \textbf{calculation time}: time the framework actually executed the algorithm
	\item \textbf{overhead}: time difference between execution time and calculation time \newline (time to read the input graph, initialization, etc.)
\end{itemize}

@@

\section{Galois With Hugepages}
\begin{multicols}{2}

\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}
		\toprule
		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/\\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 \\
		& orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5 \\
		& wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1 \\
		& twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1 \\
		& rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4 \\
		& friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5 \\
		& rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1 \\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR Pull}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 \\
		& orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6 \\
		& wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4 \\
		& twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3 \\
		& rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1 \\
		& friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1 \\
		& rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4 \\
		\bottomrule
\end{tabular}

	\includegraphics[width=0.7\linewidth]{../../plots/singleNodeSSSPGaloisHPThreads.png}
	SSSP

	\includegraphics[width=0.7\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
	PR Pull
\end{multicols}

>>>>

\section{Evaluation}
\begin{multicols}{2}
\noindent 5 Machines, with
\begin{itemize}
	\item 96 cores, of which 48 virtual
	\item 256 GB of RAM each, one machine only 128 GB
	\item Ubuntu 18.04.2 LTS
\end{itemize}
\noindent Measurements:
\begin{itemize}
	\item \textbf{execution time}: time from start to finish of the console command
	\item \textbf{calculation time}: time the framework actually executed the algorithm
	\item \textbf{overhead}: time difference between execution time and calculation time \newline (time to read the input graph, initialization, etc.) -- brauchen wir das überhaupt?
\end{itemize}

@@

\section{Galois With Hugepages}
\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}rc}
		\toprule
		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}&\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/&\\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 & 
		\multirow{7}{8cm}{\includegraphics[width=5.5cm]{../../plots/singleNodeSSSPGaloisHPThreads.png}}
		\\
		& orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5 & \\
		& wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1 & \\
		& twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1 & \\
		& rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4 & \\
		& friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5 & \\
		& rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1 & \\
		\midrule

		\bottomrule
\end{tabular}

\section{Galois With Hugepages}
\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}rc}
\toprule
		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}&\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/&\\
		\midrule
	\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR Pull}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 & \\
		& orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6 & \\
		& wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4 & \\
		& twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3 & \\
		& rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1 & \\
		& friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1 & \\
		& rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4 & \\
	\bottomrule
\end{tabular}

	\includegraphics[width=1cm]{../../plots/singleNodeSSSPGaloisHPThreads.png}

	%\includegraphics[width=0.7\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
